Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches

### 2021-04-20 paper.tex
Update on Overleaf.

\documentclass[10pt,journal,compsoc]{IEEEtran}
\usepackage{subfiles}
\usepackage{url}
\usepackage[pdftex]{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{subfig}
\usepackage[noend]{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:~}}
\renewcommand{\algorithmicensure}{\textbf{Output:~}}
\newcommand\ovr[1]{\overrightarrow{#1}}
\newcommand\myeq{\mkern1.5mu{=}\mkern1.5mu}
\usepackage{booktabs}
\usepackage{array}
\usepackage{color}
\usepackage{listings}
\usepackage{placeins}
\usepackage{enumitem}
%%%%%%
% notation 
%%%%%
\ifCLASSOPTIONcompsoc
  \usepackage[nocompress]{cite}
\else
  \usepackage{cite}
\fi

@@

Efficient information/influence dissemination in a network is an important research area with several applications in various fields, such as viral marketing~\cite{leskovec2007dynamics, trusov2009effects}, social media analysis~\cite{zeng2010social, moreno2004dynamics}, and recommendation systems~\cite{lu2012recommender}.
As the study of these networks is imperative for educational, political, economic, and social purposes, a high-quality seed set to initiate the diffusion may have vital importance.
Furthermore, since the diffusion analysis may be time-critical, or increasing the influence coverage may be too expensive, novel and efficient approaches to find good vertex sets that propagate the information/influence effectively are essential.

@@

\begin{itemize}
\item We propose \acro\footnote{\url{https://github.com/ggokturk/infuser}}, an open-source, blazing-fast, sketch-based and accurate Influence Maximization algorithm. The proposed scheme samples the edges as they are traversed across several simulations. Thus, sampling, diffusion, and count-distinct processes are fused for all simulations.

@@

\item We evaluate the performance, memory consumption, and influence score with sketch- and approximation-based state-of-the-art influence maximization algorithms, namely {\sc Skim}~\cite{cohen2014sketch}, {\sc Tim+}~\cite{tim} and {\sc Imm}~\cite{minutoli2019fast}, to accurately position the performance of \acro{} within the IM literature. The experiments show that \acro is $\minspeedup\times$—$\maxspeedup\times$ faster than a state-of-the-art sketch-based algorithm while having almost the same quality with the approximation-based algorithms in terms of influence, and using a comparable amount of memory.

@@

Let $G = (V,E)$ be a directed graph where the $n$ vertices in $V$ represent the agents, and $m$ edges in $E$ represent the relations among them. An edge $(u,v) \in E$ is an {\em incoming} edge for $v$ and an {\em outgoing} edge of $u$. The {\em incoming} neighborhood of a vertex $v \in V$ is denoted as $\Gamma_{G}(v) = \{u: (u,v) \in E\}$. A graph $G' = (V',E')$ is a sub-graph of $G$ if $V' \subseteq V$ and $E' \subseteq E$. The diffusion probability on the edge $(u, v) \in G$ is noted as $w_{u,v}$, where $w_{u,v}$ can be determined either by the diffusion model or according to the strength of $u$ and $v$'s relationship in the data.

\begin{table}[!ht]
    \caption{Table of notations}
    \label{tab:notation}
    \centering
    \begin{tabular}{|l|p{0.7\linewidth}|}
        \hline
        Variable & Definition  \\
        \hline
        \kktodo{uzerinden 
        gecelim}\ggx{A ekledim, S' uygun olur mu karar veremedim.}\\
        $G = (V,E)$     & Graph $G$ with vertices $V$ and edges $E$ \\
        $A_G(u)$   & Neighborhood of $u$ in graph $G$, the endpoints of its outgoing edges\\ %%FIXME
        $\Gamma_G(u)$   & Neighborhood of $u$ in graph $G$, the endpoints of its incoming edges\\ %%FIXME
        $w_{u,v}$       & Probability of $u$ directly influencing $v$ \\
        %$SCC(v) $       & Strongly connected component of vertex $v$\\
        $R_{G}(v)$      & Reachability set of vertex $v$ on graph $G$\\
%        $\overline{R_{G}(v)} & Complement of the vertex set $R_{G}(v)$\\
        \hline\hline
        $S$             & Seed set to maximize influence\\
        $K$             & Size of the seed set\\
        $\mathcal{R}$   & Number of Monte-Carlo simulations performed\\
        $\sigma_{G}(S)$ & The influence score of $S$ in $G$, i.e., expected number of vertices reached from $S$ in $G$\\
        % $\sigma_{G}{(S,v)}$          & Marginal influence gain by adding vertex $v$ to seed set $S$\\
        \hline\hline
        $w_{u,v}$             & Sampling probability for the edge $(u,v)$\\
        $P(s,v)_r $     & Random probability generated for selecting edge vertices $s$ to $v$ in simulation $r$\\
        $h(u,v)$        & Hash function for edge $\{u,v\}$\\
        $h_{max}$       & Maximum value hash function $h$ can return\\
        %$X_r$           & Random number/hash generated for simulation $r$  \\
        \hline\hline
        $e$             & Estimated reachability set size\\
        % $[a, \ldots, a]_B$      & Vector of size $B$, contains all $a$\\
        $M_u[j]$        & $j$th sketch register for vertex $u$\\
        $\varsigma $    & Influence gained before last sketch build\\
        $\sigma $       & Influence Score\\
        $\delta$        & Marginal Gain after last sketch build\\
        $Err_l$         & Local estimation error of the sketch\\
        $Err_g$         & Global estimation error of the sketch\\
        $\epsilon_{g}$    & Global estimation error threshold\\
        $\epsilon_{l}$    & Local estimation error threshold\\ 
        $\epsilon_{c}$    & Non-convergenced vertex threshold\\
      %  $x[[i, j]]$   & Slice of vector  $x$ between indices $i$ and $j$, not including $j$ \\ 
        \hline         
    \end{tabular}
\end{table}
\subsection{Influence Maximization}

@@

\begin{figure}[!ht] 
    \centering
  \subfloat[\small{IC}\label{fig:ic}]{%
       \includegraphics[width=0.37\linewidth]{images/ic.pdf}}
  \subfloat[\small{WC}\label{fig:wc}]{%
        \includegraphics[width=0.37\linewidth]{images/wc.pdf}}
    \\% IMAGES HERE
  \caption{\protect\subref{fig:ic} 
\kktodo{a parti nonuniform weight olsun}\ggx{done.} The directed graph $G = (V, E)$ for Independent Cascade with independent diffusion probabilities. 
\protect\subref{fig:wc}
The directed graph for WC is obtained by setting the diffusion probabilities of incoming edges to $1 / |\Gamma_G(v)|$ for each vertex $v \in V$. \kktodo{bu (4,1) kenarinin agirligi 1 degil mi?}\ggx{done.} 
  }
  %\label{fig_ic_model} 
  \label{fig:xx} 
\end{figure}

@@

\item The {\bf Weighted Cascade}  model is a variant of the independent cascade that uses the structural properties of vertices to set the edge weights as shown in Figure~\ref{fig:wc}.
The method, as described in~\cite{kempe2003maximizing}, sets $w_{u, v} = 1 / d_v$ where $d_v$ is the number 
of incoming edges of $v$~(which in the original graph is equal to $\Gamma _G(v)$).
Therefore, if $v$ has $\ell$ neighbors activated in the last round, its probability of activation in the new round is $1-( 1-1 / d_v)^\ell$. 
\kktodo{bu tanim [7]'dekine uymuyor. Orada undirected graph var }\ggx{fixed.} 
% Note that the model is originally defined for undirected graphs in~\cite{kempe2003maximizing}. However, the definition above is consistent since one can consider each~(undirected) edge as two directed edges.

@@

\item{\bf Linear threshold} generalizes the independent cascade model and activates the vertex $v$ once the cumulative activation coming from its neighbors exceeds a given threshold $\theta_v$. 
All the $(u, v)$ edges with active $u$ vertices are taken into account in the process. Vertex $v$ is activated when the total activation probability through these edges exceeds $\theta_v$~\cite{kempe2003maximizing}.  
Therefore, the independent cascade model is a special variant of the linear threshold model with $\theta_v = 0$. 
\end{itemize}

%As a generalization of the above-mentioned models, {\bf triggering} has also been proposed by Kempe~et~al.~\cite{kempe2003maximizing}. In this model, each neighbor has a probability to influence the vertex $v$. The diffusion process chooses a random subset of vertices called the {\em triggering set} to activate the vertices at each instance.
The complexity analysis stays consistent for many diffusion models, including {\em Independent Cascade}~(IC), {\em Weighted Cascade}~(WC), and {\em Linear Threshold}~(LT)  models; the time complexity of the greedy algorithm, estimating the $\sigma$ influence score, running $R$ simulations, and selecting $K$ seed vertices is $\mathcal{O}(KRn\sigma)$ for a graph with $n$ vertices. \kktodo{bu son cumle dogru mu}\ggx{Aklima tersini dogrulayacak bir ornek gelmiyor hocam. Dogru olmali.} We concentrate on the IC model in this paper, but the proposed methods are also relevant to other models in the literature.

\subsection{Count-Distinct Sketches}\label{sec:sketch}
The {\em distinct element count} problem focuses on finding the number of distinct elements in a stream where the elements are coming from a universal set ${\cal U}$. Finding the number of vertices to be influenced of a candidate seed vertex, i.e., the cardinality of the {\em reachability set}, is a similar problem. For each sample subgraph, the number of visited vertices is calculated while traversing the subgraphs starting from the candidate vertex. Note that an exact computation of set cardinality requires memory proportional to the cardinality which is ${\mathcal O}(|{\cal U}|)$.

The reachability set of a vertex is the union of all its connected vertices (via outgoing edges). Many IM kernels exploit this property to some degree. The methods based on {\em reverse reachability} \cite{borgs2014maximizing} \kktodo{cite}\ggx{done.} 
%and {\em bottom-up traversal} \\kktodo{cite} \ggx{buna referans dusunmem gerekli}
utilize this property directly to merge the reachability sets of connected vertices to estimate the number of vertices influenced. {\em MixGreedy} \cite{MixGreedy} \kktodo{cite}\ggx{cited.} goes one step further; it utilizes the fact that for an undirected graph, all vertices in a connected component have the same reachability set. Therefore, all the reachability sets within a single sample subgraph can be found via a single graph traversal.

For directed graphs, storing reachability sets for all vertices and merging these sets are infeasible for nontrivial graphs. 
If one-hot vectors are used to store the reachability sets for constant insertion time, $\mathcal{O}(n^2\mathcal{R})$ bits of memory is required where each merge operation has $\mathcal{O}(n)$ time complexity. 
If disjoints sets are used for storing reachability sets; $\mathcal{O}(n{\sigma}\mathcal{R})$ \kktodo{Gokhan bunu aciklayalim, bir de $\bar{\sigma}$ nedir}\ggx{estimated influence} memory is required to store all reachability sets, and each merge operation has $\mathcal{O}({\tt Ack}(\sigma))$ complexity where ${\tt Ack}$ is the Ackermann\cite{ackermann1928hilbertschen} function. \kktodo{bu Ackermann'a atif verelim}.\ggx{done.}

Count-Distinct Sketches can be leveraged to efficiently estimate the cardinality of reachability sets; for instance, the Flajolet–Martin~(FM) sketch~\cite{flajolet1985probabilistic} can do this with a constant number, $J$, of registers. Furthermore, the union of two sketches can be computed in constant time. The FM sketch simply stores that how rare the elements are in a stream. The rarity of the elements is estimated by counting the maximum number of leading zeros in the hash values of the stream elements. Initially, each register is initialized with zero. The items are hashed one by one and the length of the longest all-zero prefix is stored in the register. With a single register, the cardinality estimation can be done by computing the power $2^\ell$ where $\ell$ is the value in the register.

@@

In this work, we utilize a variant of Flajolet–Martin sketch; since multiple Monte-Carlo simulations are performed to calculate the estimated influence, we use one register per simulation and take the average length of the longest leading zeros. Two given FM sketches $M_u$ and $M_v$ can be merged, i.e., their union $M_{uv}$ can be computed by taking the pairwise maximums of their registers. Formally; 
\begin{equation}
\label{eq:sketch-merge}
    M_{uv}[j] = \max(M_u[j], M_v[j]),~1 \leq j \leq J.
\end{equation} 
In our implementation, the merge operations are performed if and only if there is an edge between the vertices in respective samples \kktodo{burada simulations yaziyordu, anlamadim, iki simulation arasinda nasil edge olur - o yuzden vertex yazdim}. \ggx{ j'th sampleda vertexler arasında sampled edge olmasını kastetmiştim. Yanlis olmus.}

\section{Error-Adaptive Influence Maximization}\label{sec:method}

@@

\acro first performs a diffusion process; the process starts with per-vertex sketches that are initialized with the hash value of the corresponding vertex~(i.e., every vertex reaches to itself). Then, for all the (sampled) edges ($u, v$), i.e., the ones that contribute to the diffusion for this simulation, the sketch of the source vertex $u$ is merged into that of the target vertex $v$ until all sketch registers for all the vertices converge. The merge operation utilized in this process is slightly different than the conventional one and retrofitted to mimic the IC diffusion.

Throughout the process, each register is used only for a single sample/simulation. 
% A merge operation for an edge ($u, v$) of the graph is performed on $v$'s register if and only if the edge exists in the sample and \kktodo{bunu da degistirdim}\ggx{biz bunu yapmiyoruz, ben burada kayboldum.} $u$ is {\em live} in the current iteration. 
A merge operation between sketch $M_u$,$M_v$ of vertices $u$,$v$,is only performed on $j$th register if there is a live edge between $u,v$ in sample $j$.

This process iteratively relays the reachability information among the vertices. At each iteration, vertices neighbors' reachability sets are added to their sketches.
%At each iteration, the sketches of the existing reachable vertices are modified. \kktodo{onceki cumleyi de degistirdim - dogru mu} \ggx{her vertex başkasına reachable olabilir, son cumleyi çıkartabilirz}
Instead of simulating the diffusion sample-by-sample, vertex-by-vertex, or path-by-path, all the influence that passes through the edges in a single step is processed together. 
This recursive formulation of the influence allows us to estimate the marginal influence for all vertices very fast. 
After the computation of reachability set cardinalities, \acro picks the vertex $v$ with the largest cardinality by evaluating the sketches. Then \acro calculates the reachability set of the latent seed set, i.e., the one that contains the current set and $v$, by performing Monte-Carlo simulations. The vertices in the reachability sets are removed from the live set, $L$.%labeled as {\em visited}. 
\kktodo{niye blocked, influenced desek?}\ggx{literaturde kullanilan terim o sekilde, ben visited'i tercih ederdim, algorithmaya gore live set L den çıkartıyoruz diye güncelledim.} in the respective samples. So that, in later iterations these vertices will not contribute to the marginal gain. Finally, the algorithm checks if rebuilding is necessary for the sketches based on the difference between the sketch estimate and Monte-Carlo estimate. \kktodo{yukaridaki cumlelerde bunlara isim verelim, burada soyleyelim matematiksel olarak - zaten isimleri var sanirim}.\ggx{malesef sembolleri,isimleri yok. $u \notin R_S$ şeklinde.}

\subsection{Hash-based Fused Sampling}
The probabilistic nature of cascade models requires sampling subgraphs from $G = (V, E)$ to simulate the diffusion process. If performed individually as a preprocessing step, as the literature traditionally does, the sampling stage can be expensive, furthermore, a time-wise dominating one for the overall IM kernel; first, sampling multiple sub-graphs may demand multiple passes on the graph, which can be very large, and second, if samples are memoized, the memory requirement can be a multiple of the graph size. 
In this work, we borrow the fused sampling technique from {\sc InFuseR}~\cite{infuser} which eliminates the necessity of creation and storage of the sample subgraphs in memory. 
\kktodo{burata alttaki figure atfen basitce ne oldugunu anlatan 2-3 cumle gerek} 
In figure \ref{fig:traversal}, we illustrate the fused sampling process; instead of processing samples independently as in \ref{fig:sims}, Fused-sampling approach process all samples for each edge as shown in \ref{fig:fused}. This allows us to process each edge only few times instead of traversing them repeatedly for all simulations.

\begin{figure}[!ht] 
    \centering
    %\subfloat[\label{fig:toy}]{%
    %   \includegraphics[width=0.47\linewidth]{sims-a%}}%  \\
    \subfloat[\label{fig:sims}]{%
        \includegraphics[width=0.5\linewidth]{images/samples.pdf}
    } 
    \subfloat[\label{fig:fused}]{%
     \includegraphics[width=0.5\linewidth]{images/fused.pdf}}
  \caption{
  %\protect\subref{fig:toy} The toy graph 
  \protect\subref{fig:sims} Two sampled subgraphs of the toy graph from Figure~\ref{fig:ic} with 4 vertices and 6 edges.
  \protect\subref{fig:fused} The simulations are performed in a way to be fused with sampling. Each edge is labeled with the corresponding sample/simulation IDs. 
  }
  \label{fig:traversal} 
\end{figure}

>>>>

\documentclass[10pt,journal,compsoc]{IEEEtran}
\usepackage{subfiles}
\usepackage{url}
\usepackage[pdftex]{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{subfig}
\usepackage[noend]{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:~}}
\renewcommand{\algorithmicensure}{\textbf{Output:~}}
\newcommand\ovr[1]{\overrightarrow{#1}}
\newcommand\myeq{\mkern1.5mu{=}\mkern1.5mu}
\usepackage{booktabs}
\usepackage{array}
\usepackage{color}
\usepackage{listings}
\usepackage{placeins}
\usepackage{enumitem}
\usepackage{balance}

%%%%%%
% notation 
%%%%%
\ifCLASSOPTIONcompsoc
  \usepackage[nocompress]{cite}
\else
  \usepackage{cite}
\fi

@@

Efficient information/influence dissemination in a network is an important research area with several applications in various fields, such as viral marketing~\cite{leskovec2007dynamics, trusov2009effects}, social media analysis~\cite{zeng2010social, moreno2004dynamics}, and recommendation systems~\cite{lu2012recommender}.
As the study of these networks is imperative for educational, political, economic, and social purposes, a high-quality seed set to initiate the diffusion may have vital importance.
Furthermore, since the diffusion analysis may be time-critical, or increasing the influence coverage may be too expensive, novel and efficient approaches to find good vertex sets that propagate the information effectively are essential.

@@

\begin{itemize}
\item We propose \acro\footnote{\scriptsize{\url{https://github.com/ggokturk/infuser}}}, an open-source, blazing-fast, sketch-based and accurate Influence Maximization algorithm. The proposed scheme samples the edges as they are traversed across several simulations. Thus, sampling, diffusion, and count-distinct processes are fused for all simulations.

@@

\item We evaluate the performance, memory consumption, and influence score with sketch- and approximation-based state-of-the-art influence maximization algorithms, namely {\sc Skim}~\cite{cohen2014sketch}, {\sc Tim}~\cite{tim} and {\sc Imm}~\cite{minutoli2019fast}, to accurately position the performance of \acro{} within the IM literature. The experiments show that \acro is $\minspeedup\times$—$\maxspeedup\times$ faster than a state-of-the-art sketch-based algorithm while having the same quality with the approximation-based algorithms w.r.t. influence, and using a comparable amount of memory.

@@

Let $G = (V,E)$ be a directed graph where the $n$ vertices in $V$ represent the agents, and $m$ edges in $E$ represent the relations among them. An edge $(u,v) \in E$ is an {\em incoming} edge for $v$ and an {\em outgoing} edge of $u$. The {\em incoming} neighborhood of a vertex $v \in V$ is denoted as $\Gamma^-_{G}(v) = \{u: (u,v) \in E\}$. Similarly, the {\em outgoing} neighborhood of a vertex $v \in V$ is denoted as $\Gamma^+_{G}(v) = \{u: (v,u) \in E\}$. A graph $G' = (V',E')$ is a sub-graph of $G$ if $V' \subseteq V$ and $E' \subseteq E$. The diffusion probability on the edge $(u, v) \in G$ is noted as $w_{u,v}$, where $w_{u,v}$ can be determined either by the diffusion model or according to the strength of $u$ and $v$'s relationship.

\begin{table}[!ht]
    \caption{Table of notations}
    \label{tab:notation}
    \centering
    \begin{tabular}{|l|p{0.7\linewidth}|}
        \hline
        Variable & Definition  \\
        \hline
        %\kktodo{uzerinden 
        %gecelim}\ggx{A ekledim, S' uygun olur mu karar veremedim.}\\
        $G = (V,E)$     & Graph $G$ with vertices $V$ and edges $E$ \\
         $\Gamma^+_G(u)$ & The set of vertices $v$ where $(u,v) \in E$ \\ %%FIXME
        $\Gamma^-_G(u)$  &The set of vertices $v$ where $(v, u) \in E$\\ %%FIXME
        $w_{u,v}$       & Probability of $u$ directly influencing $v$ \\
        %$SCC(v) $       & Strongly connected component of vertex $v$\\
        $R_{G}(v)$      & Reachability set of vertex $v$ on graph $G$\\
%        $\overline{R_{G}(v)} & Complement of the vertex set $R_{G}(v)$\\
        \hline\hline
        $S$             & Seed set to maximize influence\\
        $K$             & Size of the seed set\\
        $\mathcal{R}$   & Number of Monte-Carlo simulations performed\\
        $\sigma_{G}(S)$ & The influence score of $S$ in $G$, i.e., expected number of vertices reached from $S$ in $G$\\
        % $\sigma_{G}{(S,v)}$          & Marginal influence gain by adding vertex $v$ to seed set $S$\\
        \hline\hline
        $w_{u,v}$             & Sampling probability for the edge $(u,v)$\\
        $P(s,v)_r $     & Random probability generated for selecting edge vertices $s$ to $v$ in simulation $r$\\
        $h(u,v)$        & Hash function for edge $\{u,v\}$\\
        $h_{max}$       & Maximum value hash function $h$ can return\\
        %$X_r$           & Random number/hash generated for simulation $r$  \\
        \hline\hline
        $e$             & Estimated reachability set size\\
        % $[a, \ldots, a]_B$      & Vector of size $B$, contains all $a$\\
        $M_u[j]$        & $j$th sketch register for vertex $u$\\
        $\varsigma $    & Influence gained before last sketch build\\
        $\sigma $       & Influence Score\\
        $\delta$        & Marginal gain after last sketch build\\
        $err_l$         & Local estimation error of the sketch\\
        $err_g$         & Global estimation error of the sketch\\
        $\epsilon_{g}$    & Global estimation error threshold\\
        $\epsilon_{l}$    & Local estimation error threshold\\ 
        $\epsilon_{c}$    & Non-convergenced vertex threshold\\
      %  $x[[i, j]]$   & Slice of vector  $x$ between indices $i$ and $j$, not including $j$ \\ 
        \hline         
    \end{tabular}
\end{table}
\subsection{Influence Maximization}

@@

\begin{figure}[!ht] 
    \centering
  \subfloat[\small{IC}\label{fig:ic}]{%
       \includegraphics[width=0.37\linewidth]{images/ic.pdf}}
  \subfloat[\small{WC}\label{fig:wc}]{%
        \includegraphics[width=0.37\linewidth]{images/wc.pdf}}
    \\% IMAGES HERE
  \caption{\small{\protect\subref{fig:ic} 
The directed graph $G = (V, E)$ for IC with independent diffusion probabilities. 
\protect\subref{fig:wc}
The directed graph for WC is obtained by setting the diffusion probabilities of incoming edges to $1 / |\Gamma^-_G(v)|$ for each vertex $v \in V$.% \kktodo{bu (4,1) kenarinin agirligi 1 degil mi?}\ggx{done.} 
  }}
  %\label{fig_ic_model} 
  \label{fig:xx} 
\end{figure}

@@

\item The {\bf Weighted Cascade}  model is a variant of the independent cascade that uses the structural properties of vertices to set the edge weights as shown in Figure~\ref{fig:wc}.
The method, as described in~\cite{kempe2003maximizing}, sets $w_{u, v} = 1 / d_v$ where $d_v$ is the number 
of incoming edges of $v$~(which in the original graph is equal to $\Gamma^-_G(v)$).
Therefore, if $v$ has $\ell$ neighbors activated in the last round, its probability of activation in the new round is $1-( 1-1 / d_v)^\ell$. 
%\kktodo{bu tanim [7]'dekine uymuyor. Orada undirected graph var }\ggx{fixed.} 
% Note that the model is originally defined for undirected graphs in~\cite{kempe2003maximizing}. However, the definition above is consistent since one can consider each~(undirected) edge as two directed edges.

@@

\item{\bf Linear threshold} generalizes the independent cascade model and activates the vertex $v$ once the cumulative activation coming from its neighbors exceeds a given threshold $\theta_v$. 
All the $(u, v)$ edges with active $u$ vertices are taken into account in the process. Vertex $v$ is activated when the total activation probability through these edges exceeds $\theta_v$~\cite{kempe2003maximizing}.  
Therefore, the independent cascade model is a special variant of the LT model with $\theta_v = 0$. 
\end{itemize}

%As a generalization of the above-mentioned models, {\bf triggering} has also been proposed by Kempe~et~al.~\cite{kempe2003maximizing}. In this model, each neighbor has a probability to influence the vertex $v$. The diffusion process chooses a random subset of vertices called the {\em triggering set} to activate the vertices at each instance.
The complexity analysis stays consistent for many diffusion models, including {\em Independent Cascade}, {\em Weighted Cascade}, and {\em Linear Threshold} models; the time complexity of the greedy algorithm, estimating the $\sigma$ influence score, running $R$ simulations, and selecting $K$ seed vertices is $\mathcal{O}(KRn\sigma)$ for a graph with $n$ vertices. 
We concentrate on the IC model in this paper, but although their adaptation requires some work, the proposed methods are also relevant to other models in the literature.

\subsection{Count-Distinct Sketches}\label{sec:sketch}
The {\em distinct element count} problem focuses on finding the number of distinct elements in a stream where the elements are coming from a universal set ${\cal U}$. Finding the number of vertices to be influenced of a candidate seed vertex $u$, i.e., the cardinality of $u$'s {\em reachability set}, is a similar problem. For each sample subgraph, the number of visited vertices is found while traversing the subgraphs starting from $u$. Note that an exact computation of set cardinality requires memory proportional to the cardinality, which is ${\mathcal O}(|{\cal U}|)$.

The reachability set of a vertex is the union of all its connected vertices (via outgoing edges). Many IM kernels exploit this property to some degree. The methods based on {\em reverse reachability} \cite{borgs2014maximizing} %\kktodo{cite}\ggx{done.} 
%and {\em bottom-up traversal} \\kktodo{cite} \ggx{buna referans dusunmem gerekli}
utilize this property directly to merge the reachability sets of connected vertices to estimate the number of vertices influenced. {\em MixGreedy} \cite{MixGreedy} %\kktodo{cite}\ggx{cited.} 
goes one step further; it utilizes the fact that for an undirected graph, all vertices in a connected component have the same reachability set. Therefore, all the reachability sets within a single sample subgraph can be found via a single graph traversal.

For directed graphs, storing reachability sets for all vertices and merging these sets are infeasible for nontrivial graphs. 
If one-hot vectors are used to store the reachability sets for constant insertion time, $\mathcal{O}(n^2\mathcal{R})$ bits of memory is required where each merge operation has $\mathcal{O}(n)$ time complexity. 
If disjoints sets are used for storing reachability sets; $\mathcal{O}(n{\sigma}\mathcal{R})$ 
%\kktodo{Gokhan bunu aciklayalim, bir de $\bar{\sigma}$ nedir}\ggx{estimated influence} 
memory is required to store all reachability sets, and each merge operation has $\mathcal{O}({\tt Ack}(\sigma))$ complexity where ${\tt Ack}$ is the Ackermann~\cite{ackermann} function. %\kktodo{bu Ackermann'a atif verelim}.\ggx{done.}

Count-Distinct Sketches can be leveraged to estimate reachability sets' cardinality efficiently; for instance, the Flajolet–Martin~(FM) sketch~\cite{flajolet1985probabilistic} can do this with a constant number, $J$, of registers. Furthermore, the union of two sketches can be computed in constant time. The FM sketch stores that how rare the elements are in a stream. The rarity of the elements is estimated by counting the maximum number of leading zeros in the stream elements' hash values. Initially, each register is initialized with zero. The items are hashed one by one, and the length of the longest all-zero prefix is stored in the register. With a single register, the cardinality estimation can be done by computing the power $2^\ell$ where $\ell$ is the value in the register.

@@

In this work, we utilize a variant of Flajolet–Martin sketch; since multiple Monte-Carlo simulations are performed to calculate the estimated influence, we use one register per simulation and take the average length of the longest leading zeros. Two given FM sketches $M_u$ and $M_v$ can be merged, i.e., their union $M_{uv}$ can be computed by taking the pairwise maximums of their registers. Formally; 
\begin{equation}
\label{eq:sketch-merge}
    M_{uv}[j] = \max(M_u[j], M_v[j]),~1 \leq j \leq J.
\end{equation} 
In our implementation, the merge operations are performed if and only if there is an edge between the vertices in respective samples. %\kktodo{burada simulations yaziyordu, anlamadim, iki simulation arasinda nasil edge olur - o yuzden vertex yazdim}. \ggx{ j'th sampleda vertexler arasında sampled edge olmasını kastetmiştim. Yanlis olmus.}

\section{Efficient and Error-Adaptive Influence Maximization}\label{sec:method}

@@

\acro first performs a diffusion process; the process starts with per-vertex sketches that are initialized with the hash value of the corresponding vertex~(i.e., every vertex reaches to itself). Then, for all the (sampled) edges ($u, v$), i.e., the ones that contribute to the diffusion for this simulation, the sketch of the source vertex $u$ is merged into that of the target vertex $v$ until all sketch registers for all the vertices converge. The merge operation utilized in this process is slightly different from the conventional one and retrofitted to mimic the IC diffusion.

Throughout the process, each register is used only for a single sample/simulation. 
For an edge ($u, v$) in simulation $j$ where $v$ is a live vertex, an update, i.e., a merge operation, on $u$'s register is performed on the corresponding register $M_u$[$j$], i.e., $M_u[j] = max(M_u[j],M_v[j])$.
%if and only if the edge exists in the sample and \kktodo{bunu da degistirdim}\ggx{biz bunu yapmiyoruz, ben burada kayboldum.} $u$ is {\em live} in the current iteration. 
%A merge operation between sketch $M_u$,$M_v$ of vertices $u$,$v$,is only performed on $j$th register if there is a live edge between $u,v$ in sample $j$.
That is, at each iteration, vertices (outgoing) neighbors' reachability sets are added to their sketches.
This recursive formulation of the influence iteratively relays the reachability information among the vertices, allowing us to estimate the marginal influence for all vertices very fast.
%At each iteration, the sketches of the existing reachable vertices are modified. \kktodo{onceki cumleyi de degistirdim - dogru mu} \ggx{her vertex başkasına reachable olabilir, son cumleyi çıkartabilirz}
%Instead of simulating the diffusion sample-by-sample, vertex-by-vertex, or path-by-path, all the influence that passes through the edges in a single step is processed together.

After estimating the reachability set cardinalities, \acro picks the vertex $v$ with the largest cardinality by evaluating the sketches. Then it finds the (actual) reachability set of the latent seed set, which is the union of the reachability sets of $v$ and the vertices in the seed set, by performing Monte-Carlo simulations. The vertices in this reachability set are removed from the live set $L$. %labeled as {\em visited}. 
%\kktodo{niye blocked, influenced desek?}\ggx{literaturde kullanilan terim o sekilde, ben visited'i tercih ederdim, algorithmaya gore live set L den çıkartıyoruz diye güncelledim.} 
Hence, in later iterations, these vertices will not contribute to the marginal gain. Finally, the algorithm checks if rebuilding is necessary for the sketches based on the difference between the sketch estimate and Monte-Carlo estimate. %\kktodo{yukaridaki cumlelerde bunlara isim verelim, burada soyleyelim matematiksel olarak - zaten isimleri var sanirim}.\ggx{malesef sembolleri,isimleri yok. $u \notin R_S$ şeklinde.}

\subsection{Hash-based Fused Sampling}
The probabilistic nature of cascade models requires sampling subgraphs from $G = (V, E)$ to simulate the diffusion process. If performed individually as a preprocessing step, as the literature traditionally does, sampling can be an expensive stage, furthermore, a time-wise dominating one for the overall IM kernel. We identify two main bottlenecks; first, sampling multiple sub-graphs may demand multiple passes on the graph, which can be very large and expensive to stream to the computational cores, and second, if samples are memoized, the memory requirement can be a multiple of the graph size. 
In this work, we borrow the fused-sampling technique from {\sc InFuseR}~\cite{infuser} which eliminates the necessity of creation and storage of the sample subgraphs in memory. 
In Fig.~\ref{fig:traversal}, we briefly illustrate fused-sampling; instead of processing the samples independently as in Fig.~\ref{fig:sims}, fused-sampling processes each edge concurrently for multiple simulations as shown in Fig.~\ref{fig:fused}. This allows us to process each edge only a few times instead of once for every simulation.

\begin{figure}[!ht] 
    \centering
    %\subfloat[\label{fig:toy}]{%
    %   \includegraphics[width=0.47\linewidth]{sims-a%}}%  \\
    \subfloat[\label{fig:sims}]{%
        \includegraphics[width=0.5\linewidth]{images/samples.pdf}
    } 
    \subfloat[\label{fig:fused}]{%
     \includegraphics[width=0.5\linewidth]{images/fused.pdf}}
  \caption{\small{
  %\protect\subref{fig:toy} The toy graph 
  \protect\subref{fig:sims} Two sampled subgraphs of the toy graph from Figure~\ref{fig:ic} with 4 vertices and 6 edges.
  \protect\subref{fig:fused} The simulations performed are fused with sampling. Each edge is labeled with the corresponding sample/simulation IDs. 
  }}
  \label{fig:traversal} 
\end{figure}

In \acro, when an edge of the original graph is being processed, it is processed for all possible samples. Then, it is decided to be {\it sampled} or {\it skipped} depending on the outcome of the hash-based random value for each sample. Given a graph $G = (V, E)$, for an edge $(u, v) \in E$, the hash function used is given below:
\begin{equation}
    \label{eq:hash}
    h(u,v) = \mbox{{\sc Murmur3}}(u||v)~mod~2^{31}  
\end{equation}
where $||$ is the concatenation operator. In our preliminary experiments, we have tried a set of hash algorithms. After a careful analysis, we chose {{\sc Murmur3}} due to its simplicity and good avalanche behavior with a maximum bias $0.5\%$~\cite{MurmurHash3Performance}. Although the approach as mentioned above generates a unique hash value for each edge, and hence a unique sampling probability, different simulations require different probabilities. First, a set of uniformly randomly chosen numbers $X_r \in_R [0, h_{max}]$ associated with each simulation $r$ are generated to enable this for each edge. Then the sampling probability of $(u, v)$ for simulation $r$, $P(u, v)_r$, is computed: To do this, the hash value, $h(u,v)$, is XOR'ed with  $X_r$ and the result is normalized by dividing the value to the upper limit of the hash value $h_{max}$. Formally,
\begin{equation}
    \label{eq:hash_prob}
    P(u,v)_r = \frac{X_r \oplus h(u,v)}{h_{max}}.
\end{equation}
% The edge $\{u,v\}$ is verified to be in the sample if ${\rho}(u,v)_r$ is smaller than or equal to the threshold $w_{u,v}$. 
The edge $(u,v)$ exists in the sample $r$ if and only if  ${P}(u,v)_r$ is smaller than the edge threshold $w_{u,v}$. One of this approach's benefits is that an edge can be sampled using a single XOR and compare-greater-than operation. Moreover, the corresponding control flow branch overhead can be removed using {\em conditional move} instructions.

\begin{figure}[!ht] 
    \centering
    \includegraphics[width=1\linewidth]{./images/CDF.pdf}
    \caption{\small{Cumulative probability function of hash-based sampling probabilities on various real-life networks.}}
    \label{fig:prob-cdf} 
\end{figure}
